Tree size, microhabitat, and hydraulic traits (interactively) shape drought response in a temperate broadleaf forest

### 2019-08-09 manuscript/climate_sensitivity_draft.Rmd
Update climate_sensitivity_draft.Rmd
Updated rmd file

@@

```{r, Table-cores-position, eval=TRUE, echo=FALSE, message=FALSE}
library(RCurl)
library(dplyr)
library(tidyr)
library(data.table)
library(knitr)
library(kableExtra)

species <- read.csv("D:/Dropbox (Smithsonian)/Github_Ian/McGregor_climate-sensitivity-variation/data/core_list_for_neil.csv", stringsAsFactors = FALSE)

table <- species[, c(1:3,6,17)]

positions <- read.csv(text=getURL("https://raw.githubusercontent.com/SCBI-ForestGEO/SCBI-ForestGEO-Data/master/tree_dimensions/tree_crowns/cored_dendroband_crown_position_data/dendro_cored_full.csv"))

table$position_all <- positions$crown.position[match(table$tag, positions$tag)]
table$position_all <- gsub("D", "dominant", table$position_all)
table$position_all <- gsub("C", "co-dominant", table$position_all)
table$position_all <- gsub("I", "intermediate", table$position_all)
table$position_all <- gsub("S", "suppressed", table$position_all)

table1 <- table %>%
  group_by(sp) %>%
  summarize(n_cores=n())

table2 <- table %>%
  group_by(sp, position_all) %>%
  summarize(count=n())

table2 <- spread(table2, key=position_all, value=count)
setnames(table2, old="<NA>", new="prior dead")

table2$n_cores <- table1$n_cores[match(table2$sp, table1$sp)]
table2 <- table2[, c(1,7,3,2,4:6)]
table2 <- table2[!table2$sp %in% c("frni", "pist"), ]

kable(table2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r, traits-overview, eval=TRUE, echo=FALSE, message=FALSE}
library(knitr)
library(kableExtra)

trees_all <- read.csv("tables_figures/trees_all.csv", stringsAsFactors = FALSE)

trees_all <- trees_all[!duplicated(trees_all$sp), ]

traits_table <- data.frame(
  "Trait" = c("Ring Porosity", "Percent Leaf Area", "Leaf Mass Area", "Wood density", "TLP"),
  "Unit" = c("ring, semi-ring, diffuse", "%", "g/m2", "g/cm3", "MPa"))
traits_table$abb <- c("rp", "PLA", "LMA", "WD", "TLP")

traits_table$mean <- NA
traits_table$min <- NA
traits_table$max <- NA

for (i in seq(along=traits_table$abb[2:5])){
  trait <- traits_table$abb[2:5][i]

  sub <- trees_all[grepl(trait, colnames(trees_all))]
  traits_table$mean[2:5][i] <- ifelse(grepl(trait, colnames(sub)), 
                              mean(sub[, 1], na.rm=TRUE), 
                              traits_table$mean)

  traits_table$min[2:5][i] <- ifelse(grepl(trait, colnames(sub)), 
                              min(sub[, 1], na.rm=TRUE), 
                              traits_table$min)

  traits_table$max[2:5][i] <- ifelse(grepl(trait, colnames(sub)), 
                              max(sub[, 1], na.rm=TRUE), 
                              traits_table$max)
}

traits_table[, c("mean", "min", "max")] <- 
  sapply(traits_table[, c("mean", "min", "max")], function(x)
  round(x, 2)
)
traits_table$abb <- NULL

@@

```{r, Table x, eval=TRUE, echo=FALSE, message=FALSE}
traits_test <- read.csv("tables_figures/tested_traits_all.csv")
traits_test$null_model <- gsub("resist.value ~ ", "", traits_test$null_model)
traits_test$tested_model <- NULL
traits_test$null_model_year <- gsub("resist.value ~ ", "", traits_test$null_model_year)
traits_test$tested_model_year <- NULL

kable(traits_test, booktabs=TRUE, format = "latex", caption = "All variables tested for climate sensitivity against appropriate null models, in line with hypothesis predictions. Each variable was tested for each drought scenario excepting \"year\" ") %>%
  kableExtra::landscape()
  # kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "scale_down")

>>>>

*Let's put Table 1 here. We need to give the hypotheses/ predictions here. It seems counterintuitive to put the results right up front like that, but it actually tends to be a higher-impact style of writing, and recommended [here](https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1005619).*

@@

```{r, Table-cores-position, eval=TRUE, echo=FALSE, message=FALSE}

kable(table2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```
```{r, traits-overview, eval=TRUE, echo=FALSE, message=FALSE}

@@

![Table 3 (example!)](tables_figures/Table3.png)
